\textbf{NAME OF THIS STUDY}

### 2018-11-08 submission/manuscript.Rmd
tables added

```{r model_parameters, echo=FALSE, results='asis'}
model_param <- read.table('../data/process/model_parameters.txt', header=T, sep='\t') %>% 
   select(Method, Parameter, Cross.Validation, Epochs, Scaler, Sklearn.Function) %>% 
  rename("Cross Validation"="Cross.Validation") %>%
  rename("Epoch"="Epochs") %>%
  rename("Sklearn Function"="Sklearn.Function")

Table1 <- kable(model_param, "latex", caption = "Optimized hyper-parameters, pre-processing and cross-validation methods and software implementation of the classification algorithms", booktabs = T) %>%
kable_styling(latex_options = c("striped", "scale_down"), position = "left") %>%  
 column_spec(1, width="10em") %>%
  column_spec(2, width="8em") %>% 
  column_spec(3, width="9em") %>%
  column_spec(5, width="5em") %>% 
  row_spec(1:7, align="l") %>% 
  row_spec(0,bold=TRUE)

param_range <- read.table('../data/process/model_parameters.txt', header=T, sep='\t', na.strings="", stringsAsFactors = FALSE) %>% 
  replace(is.na(.), "-") %>%  
  select(-Value, -Parameter, -Cross.Validation, -Epochs, -Scaler, -Sklearn.Function)

Table2 <- kable(param_range, "latex", caption = "The range of optimized hyper-parameters for each of the classification algorithms", booktabs = T) %>%
kable_styling(latex_options = c("striped", "scale_down"), position = "left")%>%
 column_spec(2:3, width="5em")

```
\vspace{35mm}

@@

Insert figure legends with the first sentence in bold, for example:

**Figure 1. Generalization and classification performance of modeling methods ** AUC values of all cross validation and testing performances.
```{r}
```

```{r}
Table1
```
\newpage

## References

>>>>

```{r table_1_models, echo=FALSE, results='asis'}
# We load a model parameters file to make our Table 1. Model parameters file has the information of optimized hyper-parameters, pre-processing and cross-validation methods and software implementation for all the classification algorithms.

# This file is hand-made. Therefore needs to be changed manually if new information wants to be added or information needs to be changed.

model_param <- read.table('../data/process/model_parameters.txt', header=T, sep='\t') %>% 
   select(Method, Parameter, Cross.Validation, Epochs, Scaler, Sklearn.Function) %>% 
  rename("Cross Validation"="Cross.Validation") %>%
  rename("Epoch"="Epochs") %>%
  rename("Sklearn Function"="Sklearn.Function")

             ### Table 1 generation ###

Table1 <- kable(model_param, "latex", caption = "Optimized hyper-parameters, pre-processing and cross-validation methods and software implementation of the classification algorithms.", booktabs = T, linesep = "") %>%
kable_styling(latex_options = c("striped", "scale_down"), position = "left") %>%  
 column_spec(1, width="10em") %>%
  column_spec(2, width="8em") %>% 
  column_spec(3, width="9em") %>%
  column_spec(5, width="5em") %>% 
  row_spec(1:7, align="l") %>% 
  row_spec(0,bold=TRUE)
```

```{r table_2_3_params echo=FALSE, results='asis'}
# We load a param_grid.scv file to make our Table 2 and 3. This file has the information of the ranges of the optimized hyper-parameters for each model.

# This file is generated from model_selection.py that is used to define model parameters for main.py. Therefore any changes to those files would allow us to represent them in the tables automatically.

################ Non-tree based model parameters ##############
linear_param_range <- read.table('../data/process/param_grid.csv', header=T, sep=',', na.strings="", stringsAsFactors = FALSE) %>% 
  replace(is.na(.), "-")  %>% 
  select(1:17) %>% 
   slice(1:2)

              ## Table 2 generation ##
Table2 <- kable(linear_param_range, "latex", caption = "The range of optimized hyper-parameters for logistic regression and support vector machines.", booktabs = T, col.names = NULL, linesep = "") %>%
kable_styling(latex_options = c("striped", "scale_down"), position = "left") %>% 
  add_header_above(c("Parameter", "L2 Logistic" = 4, "L1 SVM Linear" = 4, "L2 SVM Linear " = 3, "SVM RBF"=5), bold=TRUE) %>% 
  column_spec(2, border_left = T) %>%
  column_spec(6, border_left = T) %>% 
  column_spec(10, border_left = T) %>% 
  column_spec(13, border_left = T)
################ Tree based model parameters ##############
tree_param_range <- read.table('../data/process/param_grid.csv', header=T, sep=',', na.strings="", stringsAsFactors = FALSE) %>% 
  replace(is.na(.), "-")  %>% 
  select(1, 18:29) %>% 
  slice(3:9)

                  ## Table 3 generation ##
Table3 <- kable(tree_param_range, "latex", caption = "The range of optimized hyper-parameters for tree based classification algorithms.", booktabs = T, col.names = NULL, linesep = "") %>%
kable_styling(latex_options = c("striped", "scale_down"), position = "left", font_size=6) %>% 
  add_header_above(c("Parameter", "Random Forest"=5, "Decision Tree"= 4, "XGBoost"=3 ), bold=TRUE) %>% 
  column_spec(2, border_left = T) %>% 
  column_spec(7, border_left = T)%>% 
  column_spec(11, border_left = T)
```
\vspace{35mm}

@@

**Figure 1. Generalization and classification performance of modeling methods ** AUC values of all cross validation and testing performances.
\begin{center}
\includegraphics[width=7in]{../results/figures/AUC_comparison.pdf}
\end{center}

```{r}
Table1
Table2
Table3
```

### 2018-11-08 submission/manuscript.tex
tables added

Insert figure legends with the first sentence in bold, for example:

\textbf{Figure 1. Generalization and classification performance of
modeling methods } AUC values of all cross validation and testing
performances.
\includegraphics{manuscript_files/figure-latex/unnamed-chunk-1-1.pdf}

@@

\caption{\label{tab:model_parameters}Optimized hyper-parameters, pre-processing and cross-validation methods and software implementation of the classification algorithms}
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{8em}>{\raggedright\arraybackslash}p{9em}r>{\raggedright\arraybackslash}p{5em}l}
\hiderowcolors
\toprule
\textbf{Method} & \textbf{Parameter} & \textbf{Cross Validation} & \textbf{Epoch} & \textbf{Scaler} & \textbf{Sklearn Function}\\
\midrule
\showrowcolors
\multicolumn{1}{>{\raggedright\arraybackslash}p{10em}}{Logistic Regression} & \multicolumn{1}{>{\raggedright\arraybackslash}p{8em}}{C} & \multicolumn{1}{>{\raggedright\arraybackslash}p{9em}}{5-fold, 100-repeats} & \multicolumn{1}{l}{100} & \multicolumn{1}{>{\raggedright\arraybackslash}p{5em}}{MinMax} & \multicolumn{1}{l}{LogisticRegression}\\
\multicolumn{1}{>{\raggedright\arraybackslash}p{10em}}{L1 SVM Linear Kernel} & \multicolumn{1}{>{\raggedright\arraybackslash}p{8em}}{C} & \multicolumn{1}{>{\raggedright\arraybackslash}p{9em}}{5-fold, 100-repeats} & \multicolumn{1}{l}{100} & \multicolumn{1}{>{\raggedright\arraybackslash}p{5em}}{Standard} & \multicolumn{1}{l}{LinearSVC}\\
\multicolumn{1}{>{\raggedright\arraybackslash}p{10em}}{L2 SVM Linear Kernel} & \multicolumn{1}{>{\raggedright\arraybackslash}p{8em}}{C} & \multicolumn{1}{>{\raggedright\arraybackslash}p{9em}}{5-fold, 100-repeats} & \multicolumn{1}{l}{100} & \multicolumn{1}{>{\raggedright\arraybackslash}p{5em}}{Standard} & \multicolumn{1}{l}{LinearSVC}\\
\multicolumn{1}{>{\raggedright\arraybackslash}p{10em}}{SVM RBF Kernel} & \multicolumn{1}{>{\raggedright\arraybackslash}p{8em}}{C, gamma} & \multicolumn{1}{>{\raggedright\arraybackslash}p{9em}}{5-fold, 100-repeats} & \multicolumn{1}{l}{100} & \multicolumn{1}{>{\raggedright\arraybackslash}p{5em}}{Standard} & \multicolumn{1}{l}{SVC}\\
\multicolumn{1}{>{\raggedright\arraybackslash}p{10em}}{Decision Tree} & \multicolumn{1}{>{\raggedright\arraybackslash}p{8em}}{max\_depth, min\_samples\_split} & \multicolumn{1}{>{\raggedright\arraybackslash}p{9em}}{5-fold, 100-repeats} & \multicolumn{1}{l}{100} & \multicolumn{1}{>{\raggedright\arraybackslash}p{5em}}{MinMax} & \multicolumn{1}{l}{DecisionTreeClassifier}\\
\addlinespace
\multicolumn{1}{>{\raggedright\arraybackslash}p{10em}}{Random Forest} & \multicolumn{1}{>{\raggedright\arraybackslash}p{8em}}{n\_estimators, max\_features} & \multicolumn{1}{>{\raggedright\arraybackslash}p{9em}}{5-fold, 100-repeats} & \multicolumn{1}{l}{100} & \multicolumn{1}{>{\raggedright\arraybackslash}p{5em}}{MinMax} & \multicolumn{1}{l}{RandomForestClassifier}\\
\multicolumn{1}{>{\raggedright\arraybackslash}p{10em}}{XGBoost} & \multicolumn{1}{>{\raggedright\arraybackslash}p{8em}}{n\_estimators, colsample\_bytree, learning\_rate, subsample, max\_depth, min\_child\_weight} & \multicolumn{1}{>{\raggedright\arraybackslash}p{9em}}{5-fold, 100-repeats} & \multicolumn{1}{l}{100} & \multicolumn{1}{>{\raggedright\arraybackslash}p{5em}}{MinMax} & \multicolumn{1}{l}{XGBClassifier}\\
\bottomrule
\end{tabular}}
\end{table}

\rowcolors{2}{white}{white} \newpage

\subsection{References}\label{references}

>>>>

\textbf{Figure 1. Generalization and classification performance of
modeling methods } AUC values of all cross validation and testing
performances.

\begin{center}
\includegraphics[width=7in]{../results/figures/AUC_comparison.pdf}
\end{center}

@@

\caption{\label{tab:model_parameters}Optimized hyper-parameters, pre-processing and cross-validation methods and software implementation of the classification algorithms.}
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{8em}>{\raggedright\arraybackslash}p{9em}r>{\raggedright\arraybackslash}p{5em}l}
\hiderowcolors
\toprule
\textbf{Method} & \textbf{Parameter} & \textbf{Cross Validation} & \textbf{Epoch} & \textbf{Scaler} & \textbf{Sklearn Function}\\
\midrule
\showrowcolors
\multicolumn{1}{>{\raggedright\arraybackslash}p{10em}}{Logistic Regression} & \multicolumn{1}{>{\raggedright\arraybackslash}p{8em}}{C} & \multicolumn{1}{>{\raggedright\arraybackslash}p{9em}}{5-fold, 100-repeats} & \multicolumn{1}{l}{100} & \multicolumn{1}{>{\raggedright\arraybackslash}p{5em}}{MinMax} & \multicolumn{1}{l}{LogisticRegression}\\
\multicolumn{1}{>{\raggedright\arraybackslash}p{10em}}{L1 SVM Linear Kernel} & \multicolumn{1}{>{\raggedright\arraybackslash}p{8em}}{C} & \multicolumn{1}{>{\raggedright\arraybackslash}p{9em}}{5-fold, 100-repeats} & \multicolumn{1}{l}{100} & \multicolumn{1}{>{\raggedright\arraybackslash}p{5em}}{Standard} & \multicolumn{1}{l}{LinearSVC}\\
\multicolumn{1}{>{\raggedright\arraybackslash}p{10em}}{L2 SVM Linear Kernel} & \multicolumn{1}{>{\raggedright\arraybackslash}p{8em}}{C} & \multicolumn{1}{>{\raggedright\arraybackslash}p{9em}}{5-fold, 100-repeats} & \multicolumn{1}{l}{100} & \multicolumn{1}{>{\raggedright\arraybackslash}p{5em}}{Standard} & \multicolumn{1}{l}{LinearSVC}\\
\multicolumn{1}{>{\raggedright\arraybackslash}p{10em}}{SVM RBF Kernel} & \multicolumn{1}{>{\raggedright\arraybackslash}p{8em}}{C, gamma} & \multicolumn{1}{>{\raggedright\arraybackslash}p{9em}}{5-fold, 100-repeats} & \multicolumn{1}{l}{100} & \multicolumn{1}{>{\raggedright\arraybackslash}p{5em}}{Standard} & \multicolumn{1}{l}{SVC}\\
\multicolumn{1}{>{\raggedright\arraybackslash}p{10em}}{Decision Tree} & \multicolumn{1}{>{\raggedright\arraybackslash}p{8em}}{max\_depth, min\_samples\_split} & \multicolumn{1}{>{\raggedright\arraybackslash}p{9em}}{5-fold, 100-repeats} & \multicolumn{1}{l}{100} & \multicolumn{1}{>{\raggedright\arraybackslash}p{5em}}{MinMax} & \multicolumn{1}{l}{DecisionTreeClassifier}\\
\multicolumn{1}{>{\raggedright\arraybackslash}p{10em}}{Random Forest} & \multicolumn{1}{>{\raggedright\arraybackslash}p{8em}}{n\_estimators, max\_features} & \multicolumn{1}{>{\raggedright\arraybackslash}p{9em}}{5-fold, 100-repeats} & \multicolumn{1}{l}{100} & \multicolumn{1}{>{\raggedright\arraybackslash}p{5em}}{MinMax} & \multicolumn{1}{l}{RandomForestClassifier}\\
\multicolumn{1}{>{\raggedright\arraybackslash}p{10em}}{XGBoost} & \multicolumn{1}{>{\raggedright\arraybackslash}p{8em}}{n\_estimators, colsample\_bytree, learning\_rate, subsample, max\_depth, min\_child\_weight} & \multicolumn{1}{>{\raggedright\arraybackslash}p{9em}}{5-fold, 100-repeats} & \multicolumn{1}{l}{100} & \multicolumn{1}{>{\raggedright\arraybackslash}p{5em}}{MinMax} & \multicolumn{1}{l}{XGBClassifier}\\
\bottomrule
\end{tabular}}
\end{table}

\rowcolors{2}{white}{white}

\rowcolors{1}{white}{gray!6}

\caption{\label{tab:model_parameters}The range of optimized hyper-parameters for logistic regression and support vector machines.}
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{l|>{}llll|>{}llll|>{}lll|>{}lllll}
\hiderowcolors
\toprule
\multicolumn{1}{c}{\bfseries Parameter} & \multicolumn{4}{c}{\bfseries L2 Logistic} & \multicolumn{4}{c}{\bfseries L1 SVM Linear} & \multicolumn{3}{c}{\bfseries L2 SVM Linear } & \multicolumn{5}{c}{\bfseries SVM RBF} \\
\cmidrule(l{2pt}r{2pt}){1-1} \cmidrule(l{2pt}r{2pt}){2-5} \cmidrule(l{2pt}r{2pt}){6-9} \cmidrule(l{2pt}r{2pt}){10-12} \cmidrule(l{2pt}r{2pt}){13-17}
\showrowcolors
C & 0.01 & 0.1 & 1 & 10 & 0.001 & 0.01 & 0.1 & 1 & 0.01 & 0.1 & 1 & 1e-06 & 1e-05 & 1e-04 & 0.001 & 0.01\\
gamma & - & - & - & - & - & - & - & - & - & - & - & 1e-09 & 1e-08 & 1e-07 & - & -\\
\bottomrule
\end{tabular}}
\end{table}

\rowcolors{2}{white}{white}

\rowcolors{1}{white}{gray!6}

\caption{\label{tab:model_parameters}The range of optimized hyper-parameters for tree based classification algorithms.}
\resizebox{\linewidth}{!}{
\fontsize{6}{8}\selectfont
\begin{tabular}[t]{l|>{}lllll|>{}llll|>{}lll}
\hiderowcolors
\toprule
\multicolumn{1}{c}{\bfseries Parameter} & \multicolumn{5}{c}{\bfseries Random Forest} & \multicolumn{4}{c}{\bfseries Decision Tree} & \multicolumn{3}{c}{\bfseries XGBoost} \\
\cmidrule(l{2pt}r{2pt}){1-1} \cmidrule(l{2pt}r{2pt}){2-6} \cmidrule(l{2pt}r{2pt}){7-10} \cmidrule(l{2pt}r{2pt}){11-13}
\showrowcolors
learning\_rate & - & - & - & - & - & - & - & - & - & 0.01 & 0.1 & 1\\
max\_depth & - & - & - & - & - & 6 & 8 & 10 & 50 & 6 & 7 & 8\\
max\_features & 10 & 80 & 500 & 1000 & 1500 & - & - & - & - & - & - & -\\
min\_child\_weight & - & - & - & - & - & - & - & - & - & 1 & 2 & 3\\
min\_samples\_split & - & - & - & - & - & 10 & 25 & 50 & - & - & - & -\\
n\_estimators & 1000 & - & - & - & - & - & - & - & - & 100 & - & -\\
subsample & - & - & - & - & - & - & - & - & - & 0.7 & 0.8 & 0.9\\
\bottomrule
\end{tabular}}
\end{table}

\rowcolors{2}{white}{white}
